### 2016-12-28 paper/paper.tex
author
more structure; ack

% This file is part of the stellarTwins project.
% Copyright 2016 the authors.

\documentclass[11pt,letterpaper]{article}

@@

\section*{Title here}

\noindent
Lauren Anderson (Flatiron) \& David W. Hogg (Flatiron)

@@

>>>>

% This file is part of the stellarTwins project.
% Copyright 2016 the authors.
\documentclass[11pt,letterpaper]{article}

\newcommand{\acronym}[1]{\small{#1}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Gaia}{\project{Gaia}}

@@

\section*{A photometric method for obtaining spectroscopic parameters of stars}

\noindent
Lauren Anderson (Flatiron), David W. Hogg (Flatiron), others

@@

\paragraph{Acknowledgements:}
This project was developed in part at the 2016 NYC Gaia Sprint, hosted
by the Center for Computational Astrophysics at the Simons Foundation
in New York City.

This work has made use of data from the European Space Agency (ESA)
mission \Gaia\ (http://www.cosmos.esa.int/gaia), processed by the \Gaia
Data Processing and Analysis Consortium (\acronym{DPAC},
http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the
\acronym{DPAC} has been provided by national institutions, in particular the
institutions participating in the Gaia Multilateral Agreement.
